Tungsten Disulfides and Tungsten Oxides Core-Shell NWs

### 2015-03-29 ch-tms/tmspart.tex
Final

For \ce{MoS2}, the reaction mechanism of \ce{MoO3} to \ce{MoS2} was studied by \citeauthor{Weber1996}.\cite{Weber1996} This study presumably provided guidelines for the recent syntheses of \ce{MoS2} by sulfurization of \ce{MoO3}.\cite{Lin2012,Lee2012b,Liu2012a,Najmaei2013} Similar studies on sulfurization of \ce{WO3.H2O} to \ce{WS2} and decomposition of \ce{(NH4)2WO2S2} were also reported.\cite{VanderVlies2002,VanderVlies2002a} In combination with the knowledge from \ce{WS2}, this thesis compared those insight from several recent reports on \ce{WS2} FL. \citeauthor{Cong2013} prepared monolayer \ce{WS2} on 300 nm \ce{SiO2}-Si by sulfurization of \ce{WO3} powders in a one-end sealed tube.\cite{Cong2013} It was suggested that pre-cleaning the inner tube by \gls{ipa} and DI water could effectively increase the pressure of vapor source. This observation probably arose from the reduction of \ce{WO3} assisted by IPA and water residuals, or due to the possible presence of \ce{H2S}. Intermediate phase \ce{WO_yS_{2-y}} and \ce{WS_{2+x}} was proposed in the growth mechanism. The apex of triangles could be active site of nucleation, and \ce{WS_{2+x}} formation was confirmed by secondary ion mass spectrometry. Possible thick \ce{WS_{2+x}} flakes decomposed subsequently, leading to \gls{ml} \ce{WS2}. The substrates were thoroughly cleaned. It was mentioned that separate sulfur heating improved the PL uniformity. Sulfurization mechanism study of \ce{WO3} suggested \ce{W^{6+}} cannot be directly reduce to \ce{W^{4+}} in \ce{WS2}.\cite{VanderVlies2002,VanderVlies2002a} Tungsten oxysulfides was necessary as an intermediate phase.

\citeauthor{Peimyoo2013} prepared \ce{WS2} on \ce{SiO2}-Si using \ce{WO3} powder and sulfur at 800 \si{\degreeCelsius}, aiming at the light emission studies to clarify several contradictory reports.\cite{Peimyoo2013} Uniform PL intensity was found on the triangular \ce{WS2} flakes, in contrast to previous edge enhanced PL\cite{Berkdemir2013}. Raman spectra (532 nm) fit included $E_{2g}^1(M)$ mode at 343 cm$^{-1}$, according to the phonon dispersion calculation \cite{Molina-Sanchez2011} and experimental observation.\cite{Zeng2013a,Zhao2013,Lee2013} However, none of these experimental reports specifically mentioned $E_{2g}^1(M)$ mode. Tentative assignments of multi-phonon bands were summarized in supporting information of Ref.\cite{Zhao2013}. As to the growth setup, similar tube furnace as in Ref \cite{VanderZande2013} and \cite{Najmaei2013} was used. To gain additional wisdom on \ce{MoS2} growth, this thesis thus summarized the growth strategies in Ref \cite{VanderZande2013} and \cite{Najmaei2013} as following. \citeauthor{VanderZande2013} prepared \ce{MoS2} on 285 nm \ce{SiO2}-Si using \ce{MoO3} and S as precursors.\cite{VanderZande2013} In contrast to the seeding method adopted in Refs.\cite{Lee2013,Lee2012b}, \citeauthor{VanderZande2013} stressed the importance of carefully cleaned substrates\footnote{acetone, 2 h in \ce{H2SO4} and \ce{H2O2} (3:1) and 5 min oxygen plasma} and minimum exposure of precursor to air.\footnote{APCVD, 105 \si{\degreeCelsius} for 4 h, 700 \si{\degreeCelsius} hold for 5 min, and 10 sccm \ce{N2} within 2 inch tube. rapid cooling from 570 \si{\degreeCelsius}} Dirty substrates or old precursors led to hexagonal, 3-point star or irregular polycrystalline structures. The growth setup was similar to those in Ref.\cite{Lee2012b}. The substrate and \ce{MoO3} source distance was critical in determining the growth density. The synthesis strategy in Refs.\cite{Lee2013,Lee2012b} was briefly mentioned as well, where perylene-3,4,9,10-tetracarboxylic acid tetrapotassium salt (PTAS) treated substrate was found to promote the deposition, while KCl treated substrates did not; small carrier gas flow was preferred (1 sccm \ce{N2}). It was also noted that the \ce{MoS2} flakes morphology seemed more uniform in Ref\cite{VanderZande2013} than that in Ref\cite{Lee2012b}. On the other hand, \citeauthor{Najmaei2013} also demonstrated \ce{MoS2} FL growth by sulfurization of \ce{MoO3} nanoribbons,\cite{Najmaei2013} which was applied by dispersion and meant to control the source amount. It was found the diffusion of vapor \ce{MoO_{3-x}} was the rate-limiting step in \ce{MoS2} growth. This indicated the amount of source was critical in successful synthesis. The nucleation event was more frequently observed at substrate edges, scratches, or rough surface. Step edges was then intentionally created to facilitate the nucleation. As to the growth dynamics, it was postulated the oxysulfides (\ce{MoOS2} Raman spectra found), as intermediate phase, diffused across the bare substrates and formed triangular domains upon further sulfurization. The optimal growth conditions were 800-850 \si{\degreeCelsius}, 700 Torr, and sufficient sulfur.

\citeauthor{Zhang2013h} synthesized \ce{WS2} on sapphire (0001) using \ce{WO3} powder and sulfur as precursor under 900 \si{\degreeCelsius}.\cite{Zhang2013h} Ar slightly mixed with \ce{H2} was used to tailor the shape of \ce{WS2} flakes. It was found the source substrate distance played an important role in determining the morphology of the as-grown flakes.\footnote{There is a lattice mismatch between \ce{Al2O3} (4.785 \si{\angstrom}) and \ce{WS2} (3.153 \si{\angstrom})} The edge termination was not well studied. Raman spectra indicated a universal down-shift of $A_{1g}$ peak (1L from 418 \si{cm^{-1}} on \ce{SiO2}-Si to 416.4 \si{cm^{-1}} on sapphire). PL signal of \ce{WS2} on \ce{SiO2}-Si was stronger than that on sapphire. The visibility of \ce{WS2} on \ce{Al2O3} was poor. FET on/off ratio was about 100, indicating low carrier mobility. The other conditions included 880 \si{\degreeCelsius}, 90 mm source-to-substrate distance, and 1 inch quartz tube. The growth conditions were probably adopted from Ref.\cite{Huanga2013}.

>>>>

For \ce{MoS2}, the reaction mechanism of \ce{MoO3} to \ce{MoS2} was studied by \citeauthor{Weber1996}.\cite{Weber1996} This study presumably provided guidelines for the recent syntheses of \ce{MoS2} by sulfurization of \ce{MoO3}.\cite{Lin2012,Lee2012b,Liu2012a,Najmaei2013} Similar studies on sulfurization of \ce{WO3.H2O} to \ce{WS2} and decomposition of \ce{(NH4)2WO2S2} were also reported.\cite{VanderVlies2002,VanderVlies2002a} In combination with the knowledge from \ce{WS2}, this thesis compared those insight from several recent reports on \ce{WS2} FL. \citeauthor{Cong2013} prepared monolayer \ce{WS2} on 300 nm \ce{SiO2}-Si by sulfurization of \ce{WO3} powders in a one-end sealed tube.\cite{Cong2013} It was suggested that pre-cleaning the inner tube by \gls{ipa} and DI water could effectively increase the pressure of vapor source. This observation probably arose from the reduction of \ce{WO3} assisted by IPA and water residuals, or due to the possible presence of \ce{H2S}. Intermediate phase \ce{WO_yS_{2-y}} and \ce{WS_{2+x}} was proposed in the growth mechanism. The apex of triangles could be active site of nucleation, and \ce{WS_{2+x}} formation was confirmed by secondary ion mass spectrometry. Possible thick \ce{WS_{2+x}} flakes decomposed subsequently, leading to \gls{ml} \ce{WS2}. The substrates were thoroughly cleaned. It was mentioned that separate sulfur heating improved the \gls{pl} uniformity. Sulfurization mechanism study of \ce{WO3} suggested \ce{W^{6+}} cannot be directly reduce to \ce{W^{4+}} in \ce{WS2}.\cite{VanderVlies2002,VanderVlies2002a} Tungsten oxysulfides was necessary as an intermediate phase.

\citeauthor{Peimyoo2013} prepared \ce{WS2} on \ce{SiO2}-Si using \ce{WO3} powder and sulfur at 800 \si{\degreeCelsius}, aiming at the light emission studies to clarify several contradictory reports.\cite{Peimyoo2013} Uniform \gls{pl} intensity was found on the triangular \ce{WS2} flakes, in contrast to previous edge enhanced \gls{pl}\cite{Berkdemir2013}. Raman spectra (532 nm) fit included $E_{2g}^1(M)$ mode at 343 cm$^{-1}$, according to the phonon dispersion calculation \cite{Molina-Sanchez2011} and experimental observation.\cite{Zeng2013a,Zhao2013,Lee2013} However, none of these experimental reports specifically mentioned $E_{2g}^1(M)$ mode. Tentative assignments of multi-phonon bands were summarized in supporting information of Ref.\cite{Zhao2013}. As to the growth setup, similar tube furnace as in Ref \cite{VanderZande2013} and \cite{Najmaei2013} was used. To gain additional wisdom on \ce{MoS2} growth, this thesis thus summarized the growth strategies in Ref \cite{VanderZande2013} and \cite{Najmaei2013} as following. \citeauthor{VanderZande2013} prepared \ce{MoS2} on 285 nm \ce{SiO2}-Si using \ce{MoO3} and S as precursors.\cite{VanderZande2013} In contrast to the seeding method adopted in Refs.\cite{Lee2013,Lee2012b}, \citeauthor{VanderZande2013} stressed the importance of carefully cleaned substrates\footnote{acetone, 2 h in \ce{H2SO4} and \ce{H2O2} (3:1) and 5 min oxygen plasma} and minimum exposure of precursor to air.\footnote{APCVD, 105 \si{\degreeCelsius} for 4 h, 700 \si{\degreeCelsius} hold for 5 min, and 10 sccm \ce{N2} within 2 inch tube. rapid cooling from 570 \si{\degreeCelsius}} Dirty substrates or old precursors led to hexagonal, 3-point star or irregular polycrystalline structures. The growth setup was similar to those in Ref.\cite{Lee2012b}. The substrate and \ce{MoO3} source distance was critical in determining the growth density. The synthesis strategy in Refs.\cite{Lee2013,Lee2012b} was briefly mentioned as well, where perylene-3,4,9,10-tetracarboxylic acid tetrapotassium salt (PTAS) treated substrate was found to promote the deposition, while KCl treated substrates did not; small carrier gas flow was preferred (1 sccm \ce{N2}). It was also noted that the \ce{MoS2} flakes morphology seemed more uniform in Ref\cite{VanderZande2013} than that in Ref\cite{Lee2012b}. On the other hand, \citeauthor{Najmaei2013} also demonstrated \ce{MoS2} FL growth by sulfurization of \ce{MoO3} nanoribbons,\cite{Najmaei2013} which was applied by dispersion and meant to control the source amount. It was found the diffusion of vapor \ce{MoO_{3-x}} was the rate-limiting step in \ce{MoS2} growth. This indicated the amount of source was critical in successful synthesis. The nucleation event was more frequently observed at substrate edges, scratches, or rough surface. Step edges was then intentionally created to facilitate the nucleation. As to the growth dynamics, it was postulated the oxysulfides (\ce{MoOS2} Raman spectra found), as intermediate phase, diffused across the bare substrates and formed triangular domains upon further sulfurization. The optimal growth conditions were 800-850 \si{\degreeCelsius}, 700 Torr, and sufficient sulfur.

\citeauthor{Zhang2013h} synthesized \ce{WS2} on sapphire (0001) using \ce{WO3} powder and sulfur as precursor under 900 \si{\degreeCelsius}.\cite{Zhang2013h} Ar slightly mixed with \ce{H2} was used to tailor the shape of \ce{WS2} flakes. It was found the source substrate distance played an important role in determining the morphology of the as-grown flakes.\footnote{There is a lattice mismatch between \ce{Al2O3} (4.785 \si{\angstrom}) and \ce{WS2} (3.153 \si{\angstrom})} The edge termination was not well studied. Raman spectra indicated a universal down-shift of $A_{1g}$ peak (1L from 418 \si{cm^{-1}} on \ce{SiO2}-Si to 416.4 \si{cm^{-1}} on sapphire). \gls{pl} signal of \ce{WS2} on \ce{SiO2}-Si was stronger than that on sapphire. The visibility of \ce{WS2} on \ce{Al2O3} was poor. FET on/off ratio was about 100, indicating low carrier mobility. The other conditions included 880 \si{\degreeCelsius}, 90 mm source-to-substrate distance, and 1 inch quartz tube. The growth conditions were probably adopted from Ref.\cite{Huanga2013}.
